### 2017-04-03 notes/glossary/glossary.tex
tmp commit

>>>>

\newglossaryentry{ld}{
	name=Linkage disquilibrium,
	text=linkage disquilibrium,
	description={Correlation between nearby variants such that the alleles at neighbouring markers (on the same chromosome) are associated within a population more often than if they were unlinked}
}

\newglossaryentry{heritability}{
	name=Heritability,
	text=heritability,
	description={The proportion of the variation in a given characteristic or state that can be attributed to (additive) genetic factors}
}

### 2017-04-03 notes/notebook.tex
tmp commit

% All of the packages imported for this document:
\usepackage[utf8]{inputenc}
\usepackage{glossaries}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{url}
\usepackage{multicol}

@@

>>>>

% All of the packages imported for this document:
% \usepackage[utf8]{inputenc}
% \usepackage{glossaries}
% \usepackage{hyperref}
% \usepackage{setspace}
% \usepackage{url}
% \usepackage{multicol}

% Preamble:
\usepackage[T1]{fontenc}                                 % package for specifying output font encoding
\usepackage[acronym,style=super,nogroupskip,section=chapter]{glossaries} % package for making glossaries
\usepackage[flushleft]{threeparttablex}                  % package to add notes at the bottom of the table
\usepackage[font=footnotesize,format=hang]{caption}      % package for formatting figure caption
\usepackage[hidelinks, colorlinks]{hyperref}             % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                                % package for tweaking the chapter/section/subsection titles format
\usepackage[noabbrev,capitalise]{cleveref}               % package for referencing multiple referencing in a single \ref command
\usepackage[toc]{appendix}                               % package for making appendices
\usepackage[utf8]{inputenc}                              % package for specifying input font encoding
\usepackage{chngcntr}                                    % package for making continuous figure numbering, instead of section-based numbering
\usepackage{graphicx}                                    % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                                    % package for Times New Roman font
\usepackage{natbib}                                      % package for reference management
\usepackage{setspace}                                    % package for setting line space (used in title page)
\usepackage{xcolor,colortbl}                             % package for making colours
\usepackage{booktabs}                                    % package for better looking tables
\usepackage{longtable}                                   % package for tables that span multiple pages
\usepackage{siunitx}                                     % package for scientific notations and units
\usepackage{etoolbox}                                    % package to 'robustify' \bfseries
\usepackage{enumitem}                                    % package for tweaking lists

% Set up the hyperlinks - change the colour of the links to blue:
% \hypersetup{allcolors=blue}
\hypersetup{allcolors=black} % uncomment this line to make the hyperlinks black

\def\labelitemi{--}

@@

\bibliographystyle{BiocRefStyle}

\addcontentsline{toc}{chapter}{\bibname}

% Print out the bibliography:
\bibliography{./GWAS}
